---
title: "STOR 455 Group Project (Due 5pm on November 24th)"
subtitle: Marvel Revenue Avengers
output:
  pdf_document: default
  word_document: default
---

Liujie Zheng (730427441), Yuhan Zhou (730621041), Zhetao Zhang (730491003), Eliana Li (730521478)

# The Prediction (Required)

Our prediction of the cumulative domestic box office of "The Marvels" by December 8, 2023 is ...

# Summary of Justification (Required)

# Data (Required)

For this prediction task, we collected the **daily box office revenues** and the **Rotten Tomatoes scores** of all 33 Marvel movies. The daily box office revenues are extracted from [Box Office Mojo](https://www.boxofficemojo.com/) into the **data_raw** folder (scrapper code in **scripts/data_scrapper.py**); the Rotten Tomatoes scores are collected from [Wikipedia](https://en.wikipedia.org/wiki/List_of_Marvel_Cinematic_Universe_films) into the **metadata.csv**.

## Metadata.csv

```{r}
metadata = read.csv("metadata.csv")
dim(metadata)
```

**metadata.csv** contains 33 rows and 4 columns.

```{r}
head(metadata)
```

Each row of **metadata.csv** represents a Marvel movie. Explanation of each column:

**Movie**: Name of the Marvel movie

**Release.Date**: Release date of the movie in day-month-year

**Rotten.Tomato**: Rotten Tomatoes score

**Url**: Link to the domestic daily box office revenue

## Raw Data

Each "Movie Name.csv" file in **data_raw** folder gives the **domestic daily box office revenue** of that movie. Take the movie "Ant-Man and the Wasp" as an example:

```{r}
ant_man = read.csv("data_raw/Ant-Man and the Wasp.csv")
dim(ant_man)
```

**data_raw/Ant-Man and the Wasp.csv** contains 119 rows and 11 columns

```{r}
head(ant_man)
```

Each row represents a consecutive day. Explanation of each column:

**Date**: Screening day

**DOW**: Day of the week

**Rank**: The movie's rank in terms of box office revenue compared to other movies showing on the same day

**Daily**: The total box office revenue generated by the movie on that specific day

**X...YD**: Percent Change from Yesterday

**X...LW**: Percent Change from Last Week

**Theaters**:The number of theaters in which the movie was shown on that day

**Avg**: Average Revenue per Theater

**To.Date**: The total cumulative box office revenue for the movie up to and including that day

**Day**: The number of days since the movie was first released

**Estimated**: Whether the box office numbers are actual (false) or estimated (true) figures. 'True' suggests that the figures are preliminary and may be adjusted later, while 'False' indicates that the figures are final

For "The Marvels" movie, we have the daily box office revenue of the **first 10 days**.

```{r}
the_marvels = read.csv("data_raw/The Marvels.csv")
dim(the_marvels)
head(the_marvels)
```

## Data Cleaning

To get the data ready for analysis, we:

1) separated **Date** and **Event**

2) turned **DOW** into 1 to 7

3) turned `-` mark into `NA`

4) turned columns like **Daily**, **X\...YD** and others into numeric

The data cleaning code is in **scripts/data_cleaner.py**. Here is cleaned data of "Ant-Man and the Wasp" :

```{r}
ant_man_cleaned = read.csv("data_cleaned/Ant-Man and the Wasp_cleaned.csv")
head(ant_man_cleaned)
```

And the cleaned data of "The Marvels":

```{r}
the_marvels_cleaned = read.csv("data_cleaned/The Marvels_cleaned.csv")
head(the_marvels_cleaned)
```

## Data Visualization

Eliana Li's part

# Analysis (Required)

## Simple Linear Regression

Haoyang Li's part
